### 2021-09-15 paper/localpsf.tex
minor improvements

	By standard elliptic regularity theory, the functions $\secondgreens_i$ are in $H^3(\Omega)$, and therefore they are in $H^2(\Omega)$. By construction the functions $\secondgreens_i$ have Neumann zero boundary conditions, so $\secondgreens_i \in H^2_N(\Omega)$. Since $v_*$ is a linear combination of the functions $\secondgreens_i$ and the constant function $C(x)=1$, $v_* \in H^2_N(\Omega)$.
\end{proof}

@@

	The constraint data for the optimization problem that $w_i$ solves is the unit vector $\bm{e}^{(i)}=(0,\dots,0,1,0,\dots,0) \in \mathbb{R}^\convrank$ which has $i$th component equal to one, and all other components equal to zero. Hence
	\begin{equation*}
		\label{eq:wi_via_solution_operator}
		w_i = \mathcal{T}\left(\bm{e}^{(i)}\right).
	\end{equation*}
	The constraint data for optimization problem \eqref{eq:uy_optimization_problem} is the vector $(\convkernel_1(y), \convkernel_2(y), \dots, \convkernel_\convrank(y))$, so the solution, $\theta_*$, to optimization problem \eqref{eq:uy_optimization_problem} is given by
	\begin{equation*}
		\theta_* = \mathcal{T}\left((\convkernel_1(y), \convkernel_2(y), \dots, \convkernel_\convrank(y))\right).
	\end{equation*}
	Using the definition of $\horizinterpolant_y^\text{pc}(x)$ and linearity of $\mathcal{T}$, we have
	\begin{align*}
		\horizinterpolant_y^\text{pc}(x) &= \sum_{i=1}^\convrank \convkernel_i(y)w_i(x) \\
		&= \sum_{i=1}^\convrank \convkernel_i(y)\mathcal{T}\left(\bm{e}^{(i)}\right)(x) \\
		&= \mathcal{T}\left(\sum_{i=1}^\convrank \convkernel_i(y) \bm{e}^{(i)} \right)(x) \\
		&= \mathcal{T}\left((\convkernel_1(y), \convkernel_2(y), \dots, \convkernel_\convrank(y))\right)(x) = \theta_*(x).
	\end{align*}
	Hence $\horizinterpolant_y^\text{pc}$ is the unique solution to optimization problem \eqref{eq:uy_optimization_problem}.
\end{proof}

@@

\begin{lem}[Linearity of weighting function solution operator]
	\label{lem:T_is_linear}
	Let $\mathcal{T}:\mathbb{R}^\convrank \rightarrow H^2(\Omega)$ denote the solution operator for optimization problem \eqref{eq:generic_optimization_initial}	as a function of $f$. That is, 
	\begin{equation}
		\label{eq:opt_soln_operator}
		\mathcal{T}(f) := \horizinterpolant_*,
	\end{equation}
	where $\horizinterpolant_*$ is the minimizer of \eqref{eq:generic_optimization_initial}. The operator $\mathcal{T}$ is a linear operator.
\end{lem}

\begin{proof}
	asdf
\end{proof}

\begin{proof}[Proof of Theorem \ref{thm:smoothest_interpolant}]
	Let $f = (\convkernel_1(y), \convkernel_2(y), \dots, \convkernel_\convrank(y))$ and let $e_i = (0,\dots,0,1,0,\dots,0)$ be the length $\convrank$ vector with $i^\text{th}$ component equal to one and all other components equal to zero. The solution to optimization problem \eqref{eq:uy_optimization_problem} is given by
	\begin{align*}
		\mathcal{T}(f) &= \convkernel_1(y) \mathcal{T}(e_1) + \convkernel_2(y) \mathcal{T}(e_2) + \dots + \convkernel_\convrank(y) \mathcal{T}(e_\convrank) \\
		&= \convkernel_1(y) w_1 + \convkernel_2(y) w_2 + \dots + \convkernel_\convrank(y) w_\convrank \\
		&= \horizinterpolant_y.
	\end{align*}
	In the first line we used linearity of the solution map, $\mathcal{T}$ (Lemma \ref{lem:T_is_linear}), in the second line we used the fact that $w_i = \mathcal{T}(e_i)$, and in the third line we used the definition of $\horizinterpolant_y$ in \eqref{eq:u_defn_in_thm}.
\end{proof}

\begin{proof}[Proof of Proposition \ref{thm:wi_sum_to_one}]
	By linearity of $\mathcal{T}$ (Lemma \ref{lem:T_is_linear}), we have
	\begin{equation*}
		\sum_{i=1}^\convrank w_i(x) = \sum_{i=1}^\convrank \mathcal{T}(e_i)(x) = \mathcal{T}\left(\sum_{i=1}^\convrank e_i\right)(x) = \mathcal{T}(\bm{1})(x) = 1,
	\end{equation*}
	where $\bm{1} = (1,1,\dots,1)$ is the length $\convrank$ vector which has all components equal to one. The last equality ($\mathcal{T}(\bm{1})(x) = 1$) holds because the constant function $C \in H^2(\Omega)$, $C(x)=1$, satisfies the constraint of optimization problem \eqref{eq:generic_optimization_initial} with $f = \bm{1}$, and yields the minimum possible value of zero for the objective function.
\end{proof}

>>>>

	By standard elliptic regularity theory, the functions $\secondgreens_i$ are in $H^3(\Omega)$, and therefore they are in $H^2(\Omega)$. By construction the functions $\secondgreens_i$ have Neumann zero boundary conditions, so $\secondgreens_i \in H^2_N(\Omega)$. Since $v_*$ is a linear combination of the functions $\secondgreens_i$ and the constant function $C(x)=1$ which is in $H^2_N(\Omega)$, we have $v_* \in H^2_N(\Omega)$.
\end{proof}

@@

	The constraint data for the optimization problem that $w_i$ solves is the unit vector $\bm{e}^{(i)}=(0,\dots,0,1,0,\dots,0) \in \mathbb{R}^\convrank$ which has $i$th component equal to one, and all other components equal to zero. Hence
	\begin{equation*}
		\label{eq:wi_via_solution_operator}
		w_i = \mathcal{T}\left(\bm{e}^{(i)}\right).
	\end{equation*}
	The constraint data for optimization problem \eqref{eq:uy_optimization_problem} is the vector $(\convkernel_1(y), \convkernel_2(y), \dots, \convkernel_\convrank(y))$, so the solution, $\theta_*$, to optimization problem \eqref{eq:uy_optimization_problem} is given by
	\begin{equation*}
		\theta_* = \mathcal{T}\left((\convkernel_1(y), \convkernel_2(y), \dots, \convkernel_\convrank(y))\right).
	\end{equation*}
	Using the definition of $\horizinterpolant_y^\text{pc}(x)$ and linearity of $\mathcal{T}$, we have
	\begin{align*}
		\horizinterpolant_y^\text{pc}(x) &= \sum_{i=1}^\convrank \convkernel_i(y)w_i(x) \\
		&= \sum_{i=1}^\convrank \convkernel_i(y)\mathcal{T}\left(\bm{e}^{(i)}\right)(x) \\
		&= \mathcal{T}\left(\sum_{i=1}^\convrank \convkernel_i(y) \bm{e}^{(i)} \right)(x) \\
		&= \mathcal{T}\left((\convkernel_1(y), \convkernel_2(y), \dots, \convkernel_\convrank(y))\right)(x) = \theta_*(x).
	\end{align*}
	Thus $\horizinterpolant_y^\text{pc}$ is the unique solution to optimization problem \eqref{eq:uy_optimization_problem}.
\end{proof}

@@
